---
title: "Nkx2.2 alpha KO Morpho stats and plots"
author: "Elliott Brooks"
date: "2024-10-01"
output: html_document
---


# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("car")

library(tidyverse)
library(ggplot2)
library(cowplot)
library(viridis)
library(imputeTS)
library(BSDA)
library(ggsignif)
library(ggpattern)
library(car)
```


# Data Import and Tidying
  - Data from images were compiled from individual data spreadsheets onto the compiled data spreadsheet below
```{r import}
data <- read_csv("/Volumes/Elliott_Brooks/backup/nkx_image_data/data/nkx22_gcgicre_5wk_mstrlst.csv", 
    col_types = cols(Animal = col_character(), 
        Image = col_character(), Islet = col_character(), 
        Slide = col_character(), gcg_sst = col_double(), 
        gcg_sst_prop = col_double(), raw_sst_area = col_double(), 
        sst_area = col_double(), sst_prop = col_double(), 
        tom_sst = col_double(), tom_sst_gcg = col_double(), 
        tom_sst_gcg_mean = col_double(), 
        tom_sst_low.gcg = col_double(), tom_sst_low.gcg_prop = col_double(), 
        tom_sst_mean = col_double(),
        adj_gcg_area = col_double()))
```

## Set Genotypes as Factors
```{r}
#genotypes set as factors and ordered for appropriate genptype order in plots
data <- data %>%  mutate(Genotype = fct_relevel(Genotype, "nkx2.2flfl", 
                                                "nkx2.2plusplus_gcg.icre_tomato", 
                                                "nkx2.2flfl_gcg.icre_tomato"))


```

# Number of replicates calculation
```{r}
data %>% group_by(Animal, Genotype) %>% summarize(n()) %>% group_by(Genotype) %>% summarize(n())
```


# Islet Expression Area
- Analysize the phenotypes related to the expression area of Glucagon

## Create summary statistics and tidy for plotting
```{r}
#Create summary statistics table for expression area of all hormones measured and islet size
expression_summ <- data %>% 
  group_by(Genotype, Animal) %>% #grouped by genotype
  summarize(Islet_area = mean(islet_area, na.rm = TRUE), 
            sd_islet_expr = sd(islet_area, na.rm = TRUE)/sqrt(sum(!is.na(islet_area))),
            GCG = mean(gcg_area, na.rm = TRUE), 
            se_gcg_expr = sd(gcg_area, na.rm = TRUE)/sqrt(sum(!is.na(gcg_area))),
            INS = mean(ins_area, na.rm = TRUE), 
            se_ins_expr = sd(ins_area, na.rm = TRUE)/sqrt(sum(!is.na(ins_area))),
            SST = mean(sst_area, na.rm = TRUE), 
            se_sst_expr = sd(sst_area, na.rm = TRUE)/sqrt(sum(!is.na(sst_area))))

#create long form dataframe for plotting
expression_summ_longmean <- expression_summ %>%
  #unite means and standard errors from one hormone and genotype
  unite("islet_area", Islet_area, sd_islet_expr, sep = "_") %>%
  unite("gcg", GCG, se_gcg_expr, sep = "_") %>%
  unite("ins", INS, se_ins_expr, sep = "_") %>%
  unite("sst", SST, se_sst_expr, sep = "_") %>%
  #pivot based on Hormone/islet area
  pivot_longer(cols = c(islet_area, gcg, ins, sst), 
               names_to = "Hormone", 
               values_to = "expressio_SE") %>%
  #separate means and SEs
  separate(col = expressio_SE, into = c("Mean_Expression_Area", "SE"), sep = "_") %>%
  #redifine data columns as nnumeric (switched to character type during unite step)
  mutate(Mean_Expression_Area = as.numeric(Mean_Expression_Area),
         SE = as.numeric(SE))

#define hormone names as factor and order them
expression_summ_longmean$Hormone <- expression_summ_longmean$Hormone %>% factor( levels = c("islet_area","ins", "gcg","sst"),
                                                                       labels = c("Islet Area","INS", "GCG","SST"))


data
```


## STATISTICS: Glucagon Expression Area
-t-test was used for these analysis because it is continueous raw data that is roughly normally distributed
```{r}
#Data was split into separate dataframes by genotype for stats function input
Mut_gcg.expression_glucagon <- expression_summ_longmean %>%
  dplyr::filter(Genotype == "nkx2.2flfl_gcg.icre_tomato",
                Hormone == "GCG")

CON_gcg.expression_glucagon <- expression_summ_longmean %>%
  dplyr::filter(Genotype == "nkx2.2plusplus_gcg.icre_tomato",
                Hormone == "GCG")

flox_gcg.expression_glucagon <- expression_summ_longmean %>%
  dplyr::filter(Genotype == "nkx2.2flfl",
                Hormone == "GCG")


# QQ plot and Shapiro test to check for normality

qqPlot(expression_summ_longmean$Mean_Expression_Area)

shapiro.test(expression_summ_longmean$Mean_Expression_Area)


#T-tests for glucagon expression area between genotypes

#mutant compared to Cre control
ttest_gcg.expression_mut.con <- t.test(x = Mut_gcg.expression_glucagon$Mean_Expression_Area, 
                                       y = CON_gcg.expression_glucagon$Mean_Expression_Area)

#Create object of the output p-value for use in plotting
ttest_gcg.expression_mut.con_answer <- round(as.numeric(ttest_gcg.expression_mut.con[[3]]), digits = 3)


#mutant compared to flox control
ttest_gcg.expression_mut.flox <- t.test(x = Mut_gcg.expression_glucagon$Mean_Expression_Area, 
                                        y = flox_gcg.expression_glucagon$Mean_Expression_Area)

#Create object of the output p-value for use in plotting
ttest_gcg.expression_mut.flox_answer <- round(as.numeric(ttest_gcg.expression_mut.flox[[3]]), digits = 4)


#flox compared to Cre control
ttest_gcg.expression_flox.con <- t.test(x = flox_gcg.expression_glucagon$Mean_Expression_Area, 
                                        y = CON_gcg.expression_glucagon$Mean_Expression_Area)

#Create object of the output p-value for use in plotting
ttest_gcg.expression_flox.con_answer <- round(as.numeric(ttest_gcg.expression_flox.con[[3]]), digits = 3)




```


## PLOT: Gcg expression area 
```{r,fig.width=10, fig.height=5}


horm_expression.GCG.plot <- expression_summ_longmean %>%
  #filter for glucagon expression area data only
  dplyr::filter(Hormone == "GCG") %>%
  group_by(Genotype) %>%
  summarise(Mean_Expression_Area_se = sd(Mean_Expression_Area)/sqrt(n()),
            Mean_Expression_Area = mean(Mean_Expression_Area)) %>%
  #mutate(labelz = "GCG Expression Area") %>%
  ggplot(aes(x = Genotype, y = Mean_Expression_Area, fill = Genotype)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_jitter(data = dplyr::filter(expression_summ_longmean, Hormone == "GCG"), 
              aes(x = Genotype, y = Mean_Expression_Area), 
              size = 1, width = .1, color = "#525252") +
  #add errorbars
  geom_errorbar(aes(ymin = Mean_Expression_Area - Mean_Expression_Area_se, 
                    ymax = Mean_Expression_Area + Mean_Expression_Area_se), width=.2,
                 position=position_dodge(.9)) +
  #add p-values and comparison brackets to graph using ggsignif:: package
  ggsignif::geom_signif(comparisons = list(c(1,2), #bracket between controls
                                 c(1,3), #bracket between flox control and mutant
                                 c(2,3)), #bracket between cre control and mutant
      #call stats objects created in this sections statistics block                  
      annotations = c(paste0("N.S."),
                      paste0("p =", ttest_gcg.expression_mut.flox_answer),
                      paste0("p =", ttest_gcg.expression_mut.con_answer)),
              y_position = c(4000, 3750, 3500), #determined through trial and error
              #tip_length = c(.05,.95),
              textsize = 3) +
  theme_cowplot() +
  #scale_fill_brewer(palette = "Paired") + #dont know why this is here...
  labs(y = expression("Mean GCG Expression Area"~("\u03BCm"^2))) +  #used unicode for greek character and xpression() for superscript
  theme(axis.title.y = element_text(face = "bold", size = 15),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15)) +
  scale_fill_manual(values = c("nkx2.2flfl" = "#bababa", 
                               "nkx2.2plusplus_gcg.icre_tomato" = "#878787", 
                               "nkx2.2flfl_gcg.icre_tomato" = "#1a9641")) +
  ylim(0,4300) #based on the size of the data

  
tiff(filename = paste0("/Volumes/Elliott_Brooks/backup/nkx_image_data/img/5wk_horm_expression.GCG.plot.STAT.tiff"), 
     units = "in", width = 7, height = 4, 
     res = 300, compression = "lzw")
horm_expression.GCG.plot
dev.off() 

#Print plot
horm_expression.GCG.plot

# export for illustrator
pdf(file = "/Volumes/Elliott_Brooks/backup/nkx_image_data/img/5wk_horm_expression.GCG.plot.STAT.pdf", 
     width = 7, height = 4)
horm_expression.GCG.plot
dev.off()

```



# Glucagon+/Tomato+ cell analysis
-This analysis aims to determine if the apparnt decrease in the number of tomato-positive alpha cells is significantly decreased in mutants versus cre controls.

## Create Summary statistics and tidy for plotting
```{r}

gcg.tom_summ <- data %>%
  mutate(gcg.tom_sum = (gcg_sum*(1-gcg_only_prop))) %>% #Easier than adding up all te columns
  group_by(Genotype) %>%
  summarise(gcg.tom_mean = mean(gcg.tom_sum, na.rm = TRUE), 
            gcg.tom_SE = sd(gcg.tom_sum, na.rm = TRUE)/sqrt(sum(!is.na(gcg.tom_sum))))


write_csv(gcg.tom_summ, "/Volumes/Elliott_Brooks/backup/nkx_image_data/data/gcg.tom_summ.csv")

gcg.tom_summ_rep <- data %>%
  mutate(gcg.tom_sum = (gcg_sum*(1-gcg_only_prop))) %>% #Easier than adding up all te columns
  group_by(Genotype, Animal) %>%
  summarise(gcg.tom_mean = mean(gcg.tom_sum, na.rm = TRUE), 
            gcg.tom_SE = sd(gcg.tom_sum, na.rm = TRUE)/sqrt(sum(!is.na(gcg.tom_sum))))


write_csv(gcg.tom_summ, "/Volumes/Elliott_Brooks/backup/nkx_image_data/data/gcg.tom_summ.csv")

```

## STATISTICS: Glucagon+/Tomato+ cell analysis
```{r}
#calculate gcg.tom numbers per islet
gcg.tom_stat <- data %>%
  mutate(gcg.tom_sum = (gcg_sum*(1-gcg_only_prop)))

#Data was split into separate dataframes by genotype for stats function input
Mut_gcg.TOM <- gcg.tom_summ_rep %>%
  dplyr::filter(Genotype == "nkx2.2flfl_gcg.icre_tomato")


CON_gcg.TOM <- gcg.tom_summ_rep %>%
  dplyr::filter(Genotype == "nkx2.2plusplus_gcg.icre_tomato")

flox_gcg.TOM <- gcg.tom_summ_rep %>%
  dplyr::filter(Genotype == "nkx2.2flfl")


# QQ plot and Shapiro test to check for normality

qqPlot(gcg.tom_summ_rep$gcg.tom_mean)

shapiro.test(gcg.tom_summ_rep$gcg.tom_mean)



#T-test comparing the number of GCG+/TOM+ cells per islet

##mutant vs cre control
ttest_gcg.TOM_mut.con <- t.test(x = Mut_gcg.TOM$gcg.tom_mean, y = CON_gcg.TOM$gcg.tom_mean)

#Create object of the output p-value for use in plotting
ttest_gcg.TOM_mut.con_answer <-as.numeric(round(ttest_gcg.TOM_mut.con[[3]], digits = 4))


#print p-values
paste0("The difference in the Number of Glucagon+/Tomato+ per Islet between the mutant and Cre control is statistically significant with a p-value of ", ttest_gcg.TOM_mut.con_answer)
```

## PLOT: Glucagon+/Tomato+ cell per islets
```{r}
gcg.tom_summ.plot <- gcg.tom_summ_rep %>%
  dplyr::filter(Genotype != "nkx2.2flfl") %>%
  group_by(Genotype) %>%
  summarise(gcg.tom_se = sd(gcg.tom_mean)/sqrt(n()),
            gcg.tom_mean = mean(gcg.tom_mean)) %>%
  ggplot(aes(x = fct_relevel(Genotype, "nkx2.2plusplus_gcg.icre_tomato", "nkx2.2flfl_gcg.icre_tomato"),
             y = gcg.tom_mean, fill = Genotype)) +
  geom_bar(stat = "identity", position = position_dodge()) +
    geom_signif(comparisons = list(c(1,2)),
      annotations = paste0("p<", ttest_gcg.TOM_mut.con_answer),
              y_position = c(45),
              tip_length = c(.05,.6),
              textsize = 3) +
  geom_jitter(data = dplyr::filter(gcg.tom_summ_rep, Genotype != "nkx2.2flfl"), 
              aes(x = Genotype, y = gcg.tom_mean), size = 2, width = .1, color = "#525252") +
  geom_errorbar(aes(ymin = gcg.tom_mean - gcg.tom_se, ymax = gcg.tom_mean + gcg.tom_se), width=.2,
                position=position_dodge(.9)) +
  theme_cowplot() +
  theme(axis.title = element_text(face = "bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text = element_text(face = "bold"),
        legend.position = "none") +
  labs(y = "Avg. # GCG+/TOM+ \nCells per Islet") +
  scale_fill_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "#878787",
                               "nkx2.2flfl_gcg.icre_tomato" = "#1a9641")) +
  ylim(0,50)


tiff(filename = paste0("/Volumes/Elliott_Brooks/backup/nkx_image_data/img/5wk_gcg.tom_summ.plot.stats.tiff"), 
     units = "in", width = 3, height = 4, 
     res = 300, compression = "lzw")
gcg.tom_summ.plot
dev.off()

#print plot
gcg.tom_summ.plot


pdf(file = "/Volumes/Elliott_Brooks/backup/nkx_image_data/img/5wk_gcg.tom_summ.plot.stats.pdf", 
      width = 3, height = 4)
gcg.tom_summ.plot
dev.off()

```


# Bihormonal Cell Analysis
- These analysis calculated and plot the occurances of Glucagon/Insulin and Glucagon/Somatostatin Bihormonal cells found in the 5wk old mouse islets.

## INS/GCG: Create summary statistics and tidy for plotting
```{r}
#Replace NAs with zeros
data_no_na <- na_replace(data, fill = 0)

#Create data frame of INS/GCG data only
bihorm_ins_gcg <- data_no_na %>%
  #create combined column of count of all ins/gcg bihorm cells
  mutate(all_gcg_ins = tom_ins_gcg + `tom_ins_low-gcg`,
         #create column of proportion of glucagon cells that are ins/gcg bihormonal
         gcg_ins_bihorm = all_gcg_ins / (gcg_sum*(1-gcg_only_prop))) %>% 
  #filter out any SST data
  dplyr::filter(str_detect(Stain, "ins")) %>%
  #refine dataframe by including only pertinent columns
  dplyr::select(Genotype, Animal, all_gcg_ins, gcg_sum, gcg_ins_bihorm) %>%
  #convert any NaNs computed from calulations into zeros
  mutate_if(is.numeric, funs(ifelse(is.na(gcg_ins_bihorm), 0, .)))


######proportion of bihorm cells calcs

#compute summary statistics for the proportion of glucagon cells that are ins/gcg bihormonal
bihorm_ins_gcg_prop <- bihorm_ins_gcg %>% 
  group_by(Genotype) %>% 
  summarize(Percentage_bihorm_cells = mean(gcg_ins_bihorm),
            SE = sd(gcg_ins_bihorm, na.rm = TRUE)/sqrt(sum(!is.na(gcg_ins_bihorm)))) %>%
  mutate(Hormone = "GCG+/INS+\nTOM+")


########cells per islet calcs

#count the number of islets per genotype
bihorm_ins_gcg_isletNum <- bihorm_ins_gcg %>% 
  group_by(Genotype, Animal) %>%
  summarize(islet_number = n())

#add islet count to main ins/gcg dataframe
bihorm_ins_gcg_BYislet <- bihorm_ins_gcg %>% left_join(., bihorm_ins_gcg_isletNum, by = c("Genotype", "Animal"))

#calculate the summary statistics for number of ins/gcg bihormonal cells per islet
bihorm_ins_gcg_BYislet_summ <- bihorm_ins_gcg_BYislet %>% 
  group_by(Genotype, Animal) %>% 
  summarize(bihorm.per.islet = sum(all_gcg_ins)/islet_number,
            SE_bihorm.per.iselt =  sd(all_gcg_ins, na.rm = TRUE)/sqrt(sum(!is.na(all_gcg_ins)))) %>%
  unique()




```

## STATISTICS: INS/GCG Bihormonal cells
```{r}
#using dataframe from above calculate standard deviations from proportions column
bihorm_ins_gcg_stats_summ <- bihorm_ins_gcg %>%
  group_by(Genotype, Animal) %>% 
  summarise(sd_ins.gcg.bihorm = sd(gcg_ins_bihorm, na.rm = TRUE),
            mean_all_gcg_ins = mean(all_gcg_ins))

#create dataframe with only mutant data
Mut_ins.gcg.bihorm <- bihorm_ins_gcg_stats_summ %>%
  dplyr::filter(Genotype == "nkx2.2flfl_gcg.icre_tomato")

#create dataframe with only cre control data
CON_ins.gcg.bihorm <- bihorm_ins_gcg_stats_summ %>%
  dplyr::filter(Genotype == "nkx2.2plusplus_gcg.icre_tomato")



# QQ plot and Shapiro testto check for normality

qqPlot(bihorm_ins_gcg_stats_summ$mean_all_gcg_ins)

shapiro.test(bihorm_ins_gcg_stats_summ$mean_all_gcg_ins)


#T-test comparing the number of ins/gcg bihormonal cells in each islet

##mutant vs cre control
ttest_ins.gcg.bihorm_mut.con <- t.test(x = Mut_ins.gcg.bihorm$mean_all_gcg_ins, y = CON_ins.gcg.bihorm$mean_all_gcg_ins)

##Create object of the output p-value for use in plotting
ttest_ins.gcg.bihorm_mut.con_answer <- round(as.numeric(ttest_ins.gcg.bihorm_mut.con[[3]]), digits = 3)




```

## SST/GCG: Create summary statistics and tidy for plotting
```{r}
#Create data frame of SST/GCG data only
bihorm_sst_gcg <- data_no_na %>% 
  #create combined column of count of all sst/gcg bihorm cells
  mutate(all_gcg_sst =tom_sst_gcg + tom_sst_low.gcg, 
         #create column of proportion of glucagon cells that are sst/gcg bihormonal
         gcg_sst_bihorm = all_gcg_sst / (gcg_sum*(1-gcg_only_prop))) %>%
  #filter out any INS data
  dplyr::filter(str_detect(Stain, "sst")) %>%
  #refine dataframe by including only pertinent columns
  dplyr::select(Genotype, Animal, all_gcg_sst, gcg_sum, gcg_sst_bihorm) %>%
  #convert any NaNs computed from calulations into zeros
  mutate_if(is.numeric, funs(ifelse(is.na(gcg_sst_bihorm), 0, .)))



######proportion of bihorm cells calcs

#compute summary statistics for the proportion of glucagon cells that are sst/gcg bihormonal
bihorm_sst_gcg_prop <- bihorm_sst_gcg %>% 
  group_by(Genotype) %>% 
  summarize(Percentage_bihorm_cells = mean(gcg_sst_bihorm),            
            SE = sd(gcg_sst_bihorm, na.rm = TRUE)/sqrt(sum(!is.na(gcg_sst_bihorm)))) %>%
  mutate(Hormone = "GCG+/SST+\nTOM+")




########cells per islet calcs

#count the number of islets per genotype
bihorm_sst_gcg_isletNum <- bihorm_sst_gcg %>% 
  group_by(Genotype, Animal) %>%
  summarize(islet_number = n())

#add islet count to main ins/gcg dataframe
bihorm_sst_gcg_BYislet <- bihorm_sst_gcg %>% left_join(., bihorm_sst_gcg_isletNum, by = c("Genotype", "Animal"))

#calculate the summary statistics for number of ins/gcg bihormonal cells per islet
bihorm_sst_gcg_BYislet_summ <- bihorm_sst_gcg_BYislet %>% 
  group_by(Genotype, Animal) %>% 
  summarize(bihorm.per.islet = sum(all_gcg_sst)/islet_number,
            SE_bihorm.per.iselt =  sd(all_gcg_sst, na.rm = TRUE)/sqrt(sum(!is.na(all_gcg_sst)))) %>%
  unique()

```

## STATISTICS: SST/GCG Bihormonal cells
```{r}
#using dataframe from above calculate standard deviations from proportions column
bihorm_sst_gcg_stats_summ <- bihorm_sst_gcg %>%
  group_by(Genotype, Animal) %>% 
  summarise(sd_sst.gcg.bihorm = sd(gcg_sst_bihorm, na.rm = TRUE),
            mean_all_gcg_sst = mean(all_gcg_sst))

#create dataframe with only mutant data
Mut_sst.gcg.bihorm <- bihorm_sst_gcg_stats_summ %>%
  dplyr::filter(Genotype == "nkx2.2flfl_gcg.icre_tomato")

#create dataframe with only cre control data
CON_sst.gcg.bihorm <- bihorm_sst_gcg_stats_summ %>%
  dplyr::filter(Genotype == "nkx2.2plusplus_gcg.icre_tomato")


# QQ plot and Shapiro test to check for normality

qqPlot(bihorm_sst_gcg_stats_summ$mean_all_gcg_sst)

shapiro.test(bihorm_sst_gcg_stats_summ$mean_all_gcg_sst)




#T-test comparing the number of sst/gcg bihormonal cells in each islet

##mutant vs cre control
ttest_sst.gcg.bihorm_mut.con <- t.test(x = Mut_sst.gcg.bihorm$mean_all_gcg_sst, y = CON_sst.gcg.bihorm$mean_all_gcg_sst)

##Create object of the output p-value for use in plotting
ttest_sst.gcg.bihorm_mut.con_answer <- round(as.numeric(ttest_sst.gcg.bihorm_mut.con[[3]]), digits = 4)



```


## PLOT: INS/GCG bihormonal cells
```{r}

#plot
INS.bihomr_byIslet_plotting.plot_stripe <- bihorm_ins_gcg_BYislet_summ %>%
  #filter out flox control because it doesnt express tomato
  dplyr::filter(Genotype != "nkx2.2flfl") %>%
   group_by(Genotype) %>%
  summarize(bihorm.per.islet_mean = mean(bihorm.per.islet),
            se_bihorm.per.islet = sd(bihorm.per.islet)/sqrt(n())) %>%
  ggplot(aes(x = Genotype, y = bihorm.per.islet_mean,
             #reorder genotypes so cre control bar is first
             fill = fct_relevel(Genotype, "nkx2.2plusplus_gcg.icre_tomato", "nkx2.2flfl_gcg.icre_tomato"))) +
 geom_bar_pattern(aes(pattern = Genotype,
                      pattern_color = Genotype,
                      pattern_fill = Genotype),
           stat = "identity", 
           #pattern_fill = "black",
           pattern_angle = 45,
           pattern_density = 0.25,
           pattern_spacing = 0.1,
             #fill = "#ffffff",
           position = position_dodge()) +  
  geom_jitter(data = dplyr::filter(bihorm_ins_gcg_BYislet_summ, Genotype != "nkx2.2flfl"), 
              aes(x = Genotype, y = bihorm.per.islet), size = 2, width = .1, height = .1, color = "#525252") +
  #add errorbars
  geom_errorbar(aes(ymin = bihorm.per.islet_mean - se_bihorm.per.islet, 
                    ymax = bihorm.per.islet_mean + se_bihorm.per.islet), 
                width=.2,
                position=position_dodge(.9)) +
  #add p-values
  geom_signif(comparisons = list(c(1,2)),
              annotations = paste0("p=", wilcox_ins.gcg.bihorm_mut.con_answer),
              tip_length = c(.8,.02),
              textsize = 4) +
  theme_cowplot() +
  theme(axis.title = element_text(face = "bold"),
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank()) +
  labs(x = "GCG+/INS+\nTOM+",
       y = "Number of INS+/GCG+ Cells per Islet") +
  scale_fill_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "#878787",
                               "nkx2.2flfl_gcg.icre_tomato" = "#1a9641")) +
  scale_pattern_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "none", 
                                  "nkx2.2flfl_gcg.icre_tomato" = "stripe")) +
  scale_pattern_color_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "#ffffff",
                                       "nkx2.2flfl_gcg.icre_tomato" = "#8c96c6"))  +
  scale_pattern_fill_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "#ffffff",
                                       "nkx2.2flfl_gcg.icre_tomato" = "#8c96c6")) +
  scale_y_continuous(breaks = c(0, 1, 2, 3))

#export plot
tiff(filename = paste0("/Volumes/Elliott_Brooks/backup/nkx_image_data/img/5wk_INS_bihorm_byIslet_plotting.plot.STAT.tiff"), 
     units = "in", width = 3, height = 4, 
     res = 300, compression = "lzw")
INS.bihomr_byIslet_plotting.plot_stripe
dev.off()

pdf(file = "/Volumes/Elliott_Brooks/backup/nkx_image_data/img/5wk_INS_bihorm_byIslet_plotting.plot.STAT.pdf", 
    width = 3, height = 4)
INS.bihomr_byIslet_plotting.plot_stripe
dev.off()
```

## PLOT: SST/GCG bihormonal cells
```{r}

#plot
SST.bihomr_byIslet_plotting.plot_stripe <- bihorm_sst_gcg_BYislet_summ %>%
  #filter our flox control data
  dplyr::filter(Genotype != "nkx2.2flfl") %>%
  group_by(Genotype) %>%
  summarize(bihorm.per.islet_mean = mean(bihorm.per.islet),
            se_bihorm.per.islet = sd(bihorm.per.islet)/sqrt(n())) %>%
  ggplot(aes(x = Genotype, y = bihorm.per.islet_mean, 
             fill = fct_relevel(Genotype, "nkx2.2plusplus_gcg.icre_tomato", "nkx2.2flfl_gcg.icre_tomato"))) +
geom_bar_pattern(aes(pattern = Genotype,
                      pattern_color = Genotype,
                      pattern_fill = Genotype),
           stat = "identity", 
           #pattern_fill = "black",
           pattern_angle = 45,
           pattern_density = 0.25,
           pattern_spacing = 0.1,
             #fill = "#ffffff",
           position = position_dodge()) +
  geom_jitter(data = dplyr::filter(bihorm_sst_gcg_BYislet_summ, Genotype != "nkx2.2flfl"), 
              aes(x = Genotype, y = bihorm.per.islet), size = 2, width = .1, height = .1, color = "#525252") +
  #add errorbars
  geom_errorbar(aes(ymin = bihorm.per.islet_mean - se_bihorm.per.islet, 
                    ymax = bihorm.per.islet_mean + se_bihorm.per.islet), width=.2,
                position=position_dodge(.9)) +
  #add p-values
  geom_signif(comparisons = list(c(1,2)),
              annotations = paste0("p=", wilcox_sst.gcg.bihorm_mut.con_answer),
              tip_length = c(.9,.02),
              textsize = 4) +
  theme_cowplot() +
  theme(axis.title = element_text(face = "bold"),
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank()) +
  labs(x = "GCG+/SST+\nTOM+",
       y = "Number of SST+/GCG+ Cells per Islet") +
  scale_fill_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "#878787",
                               "nkx2.2flfl_gcg.icre_tomato" = "#1a9641"))  +
  scale_pattern_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "none", 
                                  "nkx2.2flfl_gcg.icre_tomato" = "stripe")) +
  scale_pattern_color_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "#ffffff",
                                       "nkx2.2flfl_gcg.icre_tomato" = "#fe9929"))  +
  scale_pattern_fill_manual(values = c("nkx2.2plusplus_gcg.icre_tomato" = "#ffffff",
                                       "nkx2.2flfl_gcg.icre_tomato" = "#fe9929")) +
  scale_y_continuous(breaks = c(0,1, 2,  3))

#export plot
tiff(filename = paste0("/Volumes/Elliott_Brooks/backup/nkx_image_data/img/5wk_SST_Bihorm_byIslet_plotting.plot.STAT_stripe.tiff"), 
     units = "in", width = 3, height = 4, 
     res = 300, compression = "lzw")
SST.bihomr_byIslet_plotting.plot_stripe
dev.off()

pdf(file = "/Volumes/Elliott_Brooks/backup/nkx_image_data/img/5wk_SST_Bihorm_byIslet_plotting.plot.STAT_stripe.pdf", 
     width = 3, height = 4)
SST.bihomr_byIslet_plotting.plot_stripe
dev.off()

```