---
title: "nkx2.2 alpha KO adult NKX2.2 IF analsyis"
author: "Elliott Brooks"
date: "10/28/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(ggplot2)
library(cowplot)
library(viridis)
library(imputeTS)
library(BSDA)
library(ggsignif)
library(car)
```


#data import

```{r}
nkx2_2_fl_gcg_nkx22_islet_score <- read_csv("/Volumes/Elliott_Brooks/backup/nkx_image_data/data/nkx2.2_fl_22wk_gcg_nkx22_islet_score.csv") 
```
# mafb expression in gcg tom cells: calculations, Summaries and Stats

#calculation
-calculate the proportion of GCG positive cells that co-express NKX2.2
```{r}
nkx2_2_fl_gcg_nkx22_islet_score_calcs <- nkx2_2_fl_gcg_nkx22_islet_score %>%
  dplyr::filter(!is.na(GCGpos_nkxpos)) %>%
  mutate(nkx22_gcg_proportion = GCGpos_nkxpos/(GCGpos_nkxpos+GCGpos_nkxneg)) %>%
  dplyr::filter(!is.nan(nkx22_gcg_proportion))
```

#Summaries
-Calculate the mean NKX2.2+/GCG+ cell proportion for each mouse
```{r}

nkx2_2_fl_gcg_nkx22_islet_score_SUMM <- nkx2_2_fl_gcg_nkx22_islet_score_calcs %>%
  group_by(genotype, mouse) %>%
  summarize(nkx22_gcg_proportion_mean = mean(nkx22_gcg_proportion),
            nkx22_gcg_proportion_sd = sd(nkx22_gcg_proportion),
            nkx22_gcg_proportion_se = sd(nkx22_gcg_proportion)/sqrt(n()))
  
```

#STATISTICS:
-Compare proportion of NKX2.2 positive alpha cells between Nkx2.2 alpha KO and Gcg-iCre control.
-Validates the Nkx2.2 alpha cell KO
```{r}

#Data was split into separate dataframes by genotype for stats function input
Mut_nkx.expression <- nkx2_2_fl_gcg_nkx22_islet_score_SUMM %>%
  dplyr::filter(genotype == "Mut")

CON_nkx.expression <- nkx2_2_fl_gcg_nkx22_islet_score_SUMM %>%
  dplyr::filter(genotype == "con")

########


# QQ plot and Shapiro test to check for normality

qqPlot(nkx2_2_fl_gcg_nkx22_islet_score_SUMM$nkx22_gcg_proportion_mean)

shapiro.test(nkx2_2_fl_gcg_nkx22_islet_score_SUMM$nkx22_gcg_proportion_mean)


# Run t-tests on data
ttest_nkx.expression.prop_mut.con <- t.test(x = Mut_nkx.expression$nkx22_gcg_proportion_mean, 
                                             y = CON_nkx.expression$nkx22_gcg_proportion_mean)


ttest_nkx.expression.prop_mut.con_p.value <- round(as.numeric(ttest_nkx.expression.prop_mut.con[3]), digits = 5) #print p-value



```


## PLOT: MafB expression in Glucagon+/Tomato+ cells
```{r}
nkx22_gcg.tom_summ.plot <- nkx2_2_fl_gcg_nkx22_islet_score_SUMM %>%
  group_by(genotype) %>%
  summarize(nkx22_gcg_proportion_se = sd(nkx22_gcg_proportion_mean)/sqrt(n()),
            nkx22_gcg_proportion_mean = mean(nkx22_gcg_proportion_mean)) %>%
  ggplot(aes(x = fct_relevel(genotype, "con", "Mut"),
             y = nkx22_gcg_proportion_mean, fill = genotype)) +
  geom_bar(stat = "identity", position = position_dodge()) + # bar plot
  geom_jitter(data = nkx2_2_fl_gcg_nkx22_islet_score_SUMM, 
              aes(x = genotype, y = nkx22_gcg_proportion_mean), size = 2, width = .1, color = "#525252") +
   geom_signif(comparisons = list(c(1,2)),
      annotations = paste0("p =", ttest_nkx.expression.prop_mut.con_p.value), # add p-value annotation
      tip_length = 0) +
  geom_errorbar(aes(ymin = nkx22_gcg_proportion_mean - nkx22_gcg_proportion_se, # add errorbars
                    ymax = nkx22_gcg_proportion_mean + nkx22_gcg_proportion_se), width=.2,
                position=position_dodge(.9)) +
  theme_cowplot() +
  theme(axis.title = element_text(face = "bold"),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text = element_text(face = "bold"),
        legend.position = "none") +
  labs(y = "% NKX2.2 Expression in GCG+ Cells") +
  scale_fill_manual(values = c("con" = "#878787",
                               "Mut" = "#1a9641")) +
    scale_y_continuous(labels = scales::percent, limits = c(0,1)) # convert y axis from proportion to percentage



# Export plots 

tiff(filename = paste0("/Volumes/Elliott_Brooks/backup/nkx_image_data/img/nkx22_gcg.tom_summ.plot.tiff"), 
     units = "in", width = 3, height = 4, 
     res = 300, compression = "lzw")
nkx22_gcg.tom_summ.plot
dev.off()


pdf(file = paste0("/Volumes/Elliott_Brooks/backup/nkx_image_data/img/nkx22_gcg.tom_summ.plot.pdf"), 
     width = 3, height = 4)
nkx22_gcg.tom_summ.plot
dev.off()


```
