---
title: "ITT Statistics and plotting"
author: "Elliott Brooks"
date: "2/19/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(bayestestR)
library(pROC)
library(car)

#install.packages("pROC")
#install.packages("bayestestR")


```



# data import
```{r}

ITT_masterlist <- read_csv("/Volumes/Elliott_Brooks/backup/ITT/ITT_masterlist.csv")
```

# Tidy
```{r}
ITT_masterlist_tidy <- ITT_masterlist %>%
  mutate(simple_geno = if_else(genotype == "nkx2.2flfl" | 
                                 genotype == "nkx2.2plusplus_gcg.icre",
                               "controls",
                               "nkx2.2flfl_gcg.icre")) %>%
  mutate(simple_geno = factor(simple_geno, 
                              levels = c("controls", "nkx2.2flfl_gcg.icre"),
                              labels = c("controls" = "Controls",
                                         "nkx2.2flfl_gcg.icre" = "Nkx2.2fl/fl\nGcg-iCre")))


n_df <- ITT_masterlist_tidy %>%
  group_by(simple_geno) %>%
  summarize(n = n()) %>%
  mutate(n = paste0("n=", n))

#ITT_masterlist_tidy <- ITT_masterlist_tidy %>%
 # left_join(., n_df)

```

# Fasting BG

## STATISTICS: fasting BG

```{r}

ITT_masterlist_tidy_controls <- ITT_masterlist_tidy %>%
  dplyr::filter(simple_geno == "Controls")


ITT_masterlist_tidy_mutants <- ITT_masterlist_tidy %>%
  dplyr::filter(simple_geno == "Nkx2.2fl/fl\nGcg-iCre")



# QQ plot and Shapiro test to check for normality

qqPlot(ITT_masterlist_tidy$time_0)

shapiro.test(ITT_masterlist_tidy$time_0)


# check variances
var.test(ITT_masterlist_tidy_controls$time_0, ITT_masterlist_tidy_mutants$time_0)


#Run t-test
fasting_BG_t.test <- t.test(ITT_masterlist_tidy_controls$time_0, 
                            ITT_masterlist_tidy_mutants$time_0, 
                            var.equal = F)


fasting_BG_t.test_p.val <- round(as.numeric(fasting_BG_t.test[[3]]), digits = 3)
```


## PLOT: fasting BG
```{r}

fasting_BG_plot_bar_dot <- ITT_masterlist_tidy %>%
  group_by(simple_geno) %>%
  mutate(mean_BG = mean(time_0, na.rm = TRUE),
         BG_se = sd(time_0, na.rm = TRUE)/sqrt(n())) %>%
  ggplot(aes(y = mean_BG, x = simple_geno, fill = simple_geno)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_jitter(aes( y = time_0), size = 1, width = .2, color = "#525252") +
  ggsignif::geom_signif(comparisons = list(c(1,2)),
                        annotations = fasting_BG_t.test_p.val) +
  geom_errorbar(aes(ymin = mean_BG - BG_se, ymax = mean_BG + BG_se), width=.2,
                position=position_dodge(.9)) +
  geom_text(aes(label = n, y = c(100,50), x = simple_geno), data = n_df, size = 5) +
  #geom_dotplot(fill = "black", binaxis = "y", stackdir = "center") +
  cowplot::theme_cowplot() +
  ylim(0,220) +
  scale_fill_manual(values = c("Controls" = "#878787",
                               "Nkx2.2fl/fl\nGcg-iCre" = "#1a9641")) +
  theme(legend.position = "blank",
        axis.title.x = element_blank(),
        axis.title.y = element_text(face = "bold", size = 10),
        plot.title = element_text(size = 10)) +
  labs(y = "Fasting Blood Glucose (mg/dL)",
       title = "6 hour fasting blood glucose in 5 week mice")


tiff("/Volumes/Elliott_Brooks/backup/ITT/plots/fasting_BG_plot_bar_dot.tiff", 
     units = "in", width = 4, height = 4, 
     res = 300, compression = "lzw")
fasting_BG_plot_bar_dot
dev.off()


pdf("/Volumes/Elliott_Brooks/backup/ITT/plots/fasting_BG_plot_bar_dot.pdf", 
     width = 4, height = 4)
fasting_BG_plot_bar_dot
dev.off()
```


```{r}
ITT_masterlist_tidy
```



# ITT plotting over time BG

## SUMMARY statistics
```{r}
ITT_blood.glucose_SUMM <- ITT_masterlist_tidy %>%
  dplyr::select(-percent_0, -percent_15, -percent_30, -percent_60, -percent_90, -percent_120) %>%
  pivot_longer(cols = c(time_0, time_15, time_30, time_60, time_90, time_120),
               names_to = "time",
               values_to = "blood_glucose") %>%
  group_by(simple_geno, time) %>%
  summarize(n = n(),
            mean_BG = mean(blood_glucose, na.rm = T),
            sd = sd(blood_glucose, na.rm =T),
            se = sd(blood_glucose, na.rm =T)/sqrt(n))


```

## STATISTICS

### T-tests
```{r}
ITT_masterlist_tidy_controls <- ITT_masterlist_tidy %>%
  dplyr::filter(simple_geno == "Controls")


ITT_masterlist_tidy_mutants <- ITT_masterlist_tidy %>%
  dplyr::filter(simple_geno == "Nkx2.2fl/fl\nGcg-iCre")



qqPlot(ITT_masterlist_tidy$time_0)

shapiro.test(ITT_masterlist_tidy$time_0)


var.test(ITT_masterlist_tidy_controls$time_0, ITT_masterlist_tidy_mutants$time_0)

BG_time_0_t.test <- t.test(ITT_masterlist_tidy_controls$time_0, ITT_masterlist_tidy_mutants$time_0, var.equal = F)


BG_time_0_t.test_p.val <- round(as.numeric(BG_time_0_t.test[[3]]), digits = 3)


####


#time_15

qqPlot(ITT_masterlist_tidy$time_15)

shapiro.test(ITT_masterlist_tidy$time_15)



var.test(ITT_masterlist_tidy_controls$time_15, ITT_masterlist_tidy_mutants$time_15)

BG_time_15_t.test <- t.test(ITT_masterlist_tidy_controls$time_15, ITT_masterlist_tidy_mutants$time_15, var.equal = F)


BG_time_15_t.test_p.val <- round(as.numeric(BG_time_15_t.test[[3]]), digits = 3)



####


#time_30

qqPlot(ITT_masterlist_tidy$time_30)

shapiro.test(ITT_masterlist_tidy$time_30)



var.test(ITT_masterlist_tidy_controls$time_30, ITT_masterlist_tidy_mutants$time_30)

BG_time_30_t.test <- t.test(ITT_masterlist_tidy_controls$time_30, ITT_masterlist_tidy_mutants$time_30)


BG_time_30_t.test_p.val <- round(as.numeric(BG_time_30_t.test[[3]]), digits = 3)



#time_60

qqPlot(ITT_masterlist_tidy$time_60)

shapiro.test(ITT_masterlist_tidy$time_60)


var.test(ITT_masterlist_tidy_controls$time_60, ITT_masterlist_tidy_mutants$time_60)

BG_time_60_t.test <- t.test(ITT_masterlist_tidy_controls$time_60, ITT_masterlist_tidy_mutants$time_60)


BG_time_60_t.test_p.val <- round(as.numeric(BG_time_60_t.test[[3]]), digits = 3)



#time_90

qqPlot(ITT_masterlist_tidy$time_90)

shapiro.test(ITT_masterlist_tidy$time_90)


var.test(ITT_masterlist_tidy_controls$time_90, ITT_masterlist_tidy_mutants$time_90)

BG_time_90_t.test <- t.test(ITT_masterlist_tidy_controls$time_90, ITT_masterlist_tidy_mutants$time_90)


BG_time_90_t.test_p.val <- round(as.numeric(BG_time_90_t.test[[3]]), digits = 3)



#time_120

qqPlot(ITT_masterlist_tidy$time_120)

shapiro.test(ITT_masterlist_tidy$time_120)



var.test(ITT_masterlist_tidy_controls$time_120, ITT_masterlist_tidy_mutants$time_120)

BG_time_120_t.test <- t.test(ITT_masterlist_tidy_controls$time_120, ITT_masterlist_tidy_mutants$time_120)


BG_time_120_t.test_p.val <- round(as.numeric(BG_time_120_t.test[[3]]), digits = 3)

```


### Area under the curve

##### all time points
```{r}


# Subset Data into genotype

ITT_blood.glucose_SUMM_controls <- ITT_blood.glucose_SUMM %>%
  dplyr::filter(simple_geno == "Controls") %>%
  mutate(time = as.numeric(str_remove(time, "time_"))) %>%
  arrange(time)
  


ITT_blood.glucose_SUMM_mutants <- ITT_blood.glucose_SUMM %>%
  dplyr::filter(simple_geno == "Nkx2.2fl/fl\nGcg-iCre") %>%
  mutate(time = as.numeric(str_remove(time, "time_"))) %>%
  arrange(time)

```

###### Calculate area under the curve for mean blood glucose and Standard deviation
```{r}

# Calculate area under the curve for Control data:mean blood glucose and Standard deviation

ITT_blood.glucose_controls_AUC <- bayestestR::auc(x = ITT_blood.glucose_SUMM_controls$time, y = ITT_blood.glucose_SUMM_controls$mean_BG) %>%
  data.frame() %>%
  mutate(genotype = "Controls")

ITT_blood.glucose_controls_AUC.sd <- bayestestR::auc(x = ITT_blood.glucose_SUMM_controls$time, y = ITT_blood.glucose_SUMM_controls$sd) %>%
  data.frame() %>%
  mutate(genotype = "Controls")


# Calculate area under the curve for Mutant data: mean blood glucose and Standard deviation

ITT_blood.glucose_mutants_AUC <- bayestestR::auc(x = ITT_blood.glucose_SUMM_mutants$time, y = ITT_blood.glucose_SUMM_mutants$mean_BG) %>%
  data.frame() %>%
  mutate(genotype = "Nkx2.2fl/fl\nGcg-iCre")

ITT_blood.glucose_mutants_AUC.sd <- bayestestR::auc(x = ITT_blood.glucose_SUMM_mutants$time, y = ITT_blood.glucose_SUMM_mutants$sd) %>%
  data.frame() %>%
  mutate(genotype = "Nkx2.2fl/fl\nGcg-iCre")
```


###### Combine AUC calculations
```{r}
ITT_blood.glucose_combined_AUC.sd <- rbind(ITT_blood.glucose_controls_AUC.sd, ITT_blood.glucose_mutants_AUC.sd)

colnames(ITT_blood.glucose_combined_AUC.sd)[1] <- "AUC.sd"

ITT_blood.glucose_combined_AUC <- rbind(ITT_blood.glucose_controls_AUC, ITT_blood.glucose_mutants_AUC) %>%
  left_join(., ITT_blood.glucose_combined_AUC.sd) %>%
  left_join(., unique(dplyr::select(ITT_blood.glucose_SUMM, simple_geno, n)), by = c("genotype" = "simple_geno")) %>%
  mutate(AUC.sem = AUC.sd/sqrt(n))

colnames(ITT_blood.glucose_combined_AUC)[1] <- "AUC"
```


###### Calculate t test
-using inputs of mean values, sample size and standard deviation instead of using numeric lists
```{r}
##function for t test

##https://stats.stackexchange.com/questions/30394/how-to-perform-two-sample-t-tests-in-r-by-inputting-sample-statistics-rather-tha
# m1, m2: the sample means
# s1, s2: the sample standard deviations
# n1, n2: the same sizes
# m0: the null value for the difference in means to be tested for. Default is 0. 
# equal.variance: whether or not to assume equal variance. Default is FALSE. 
t.test2 <- function(m1,m2,s1,s2,n1,n2,m0=0,equal.variance=FALSE)
{
    if( equal.variance==FALSE ) 
    {
        se <- sqrt( (s1^2/n1) + (s2^2/n2) )
        # welch-satterthwaite df
        df <- ( (s1^2/n1 + s2^2/n2)^2 )/( (s1^2/n1)^2/(n1-1) + (s2^2/n2)^2/(n2-1) )
    } else
    {
        # pooled standard deviation, scaled by the sample sizes
        se <- sqrt( (1/n1 + 1/n2) * ((n1-1)*s1^2 + (n2-1)*s2^2)/(n1+n2-2) ) 
        df <- n1+n2-2
    }      
    t <- (m1-m2-m0)/se 
    dat <- c(m1-m2, se, t, 2*pt(-abs(t),df))    
    names(dat) <- c("Difference of means", "Std Error", "t", "p-value")
    return(dat) 
}


## calculate ttest

ITT_blood.glucose_combined_AUC_t.test <- t.test2(m1 = ITT_blood.glucose_combined_AUC[1,1], 
                                                 m2 = ITT_blood.glucose_combined_AUC[2,1], 
                                          s1 = ITT_blood.glucose_combined_AUC[1,3], 
                                          s2 = ITT_blood.glucose_combined_AUC[2,3],
                                          n1 = ITT_blood.glucose_combined_AUC[1,4], 
                                          n2 = ITT_blood.glucose_combined_AUC[2,4])


```
#### 30-90
```{r}



ITT_blood.glucose_SUMM_controls_time_subset <- ITT_blood.glucose_SUMM %>%
  mutate(time = as.numeric(str_remove(time, "time_"))) %>%
  dplyr::filter(simple_geno == "Controls",
                time >= 30 & time <= 90) %>%
  arrange(time)
  


ITT_blood.glucose_SUMM_mutants_time_subset <- ITT_blood.glucose_SUMM %>%
    mutate(time = as.numeric(str_remove(time, "time_"))) %>%
  dplyr::filter(simple_geno == "Nkx2.2fl/fl\nGcg-iCre",
                time >= 30 & time <= 90) %>%
  arrange(time)
```

###### Calculate area under the curve for mean blood glucose and Standard deviation
```{r}

ITT_blood.glucose_controls_time_subset_AUC <- bayestestR::auc(x = ITT_blood.glucose_SUMM_controls_time_subset$time, 
                                                              y = ITT_blood.glucose_SUMM_controls_time_subset$mean_BG) %>%
  data.frame() %>%
  mutate(genotype = "Controls")

ITT_blood.glucose_controls_time_subset_AUC.sd <- bayestestR::auc(x = ITT_blood.glucose_SUMM_controls_time_subset$time, 
                                                                 y = ITT_blood.glucose_SUMM_controls_time_subset$sd) %>%
  data.frame() %>%
  mutate(genotype = "Controls")




ITT_blood.glucose_mutants_time_subset_AUC <- bayestestR::auc(x = ITT_blood.glucose_SUMM_mutants_time_subset$time, 
                                                             y = ITT_blood.glucose_SUMM_mutants_time_subset$mean_BG) %>%
  data.frame() %>%
  mutate(genotype = "Nkx2.2fl/fl\nGcg-iCre")

ITT_blood.glucose_mutants_time_subset_AUC.sd <- bayestestR::auc(x = ITT_blood.glucose_SUMM_mutants_time_subset$time, 
                                                                y = ITT_blood.glucose_SUMM_mutants_time_subset$sd) %>%
  data.frame() %>%
  mutate(genotype = "Nkx2.2fl/fl\nGcg-iCre")
```

###### Combine AUC calculations
```{r}
ITT_blood.glucose_combined_time_subset_AUC.sd <- rbind(ITT_blood.glucose_controls_time_subset_AUC.sd,
                                                       ITT_blood.glucose_mutants_time_subset_AUC.sd)

colnames(ITT_blood.glucose_combined_time_subset_AUC.sd)[1] <- "AUC.sd"

ITT_blood.glucose_combined_time_subset_AUC <- rbind(ITT_blood.glucose_controls_time_subset_AUC, ITT_blood.glucose_mutants_time_subset_AUC) %>%
  left_join(., ITT_blood.glucose_combined_time_subset_AUC.sd) %>%
  left_join(., unique(dplyr::select(ITT_blood.glucose_SUMM, simple_geno, n)), by = c("genotype" = "simple_geno")) %>%
  mutate(AUC.sem = AUC.sd/sqrt(n))



colnames(ITT_blood.glucose_combined_time_subset_AUC)[1] <- "AUC"
```

###### Calculate t test
-using inputs of mean values, sample size and standard deviation instead of using numeric lists
```{r}
##function for t test

##https://stats.stackexchange.com/questions/30394/how-to-perform-two-sample-t-tests-in-r-by-inputting-sample-statistics-rather-tha
# m1, m2: the sample means
# s1, s2: the sample standard deviations
# n1, n2: the same sizes
# m0: the null value for the difference in means to be tested for. Default is 0. 
# equal.variance: whether or not to assume equal variance. Default is FALSE. 
t.test2 <- function(m1,m2,s1,s2,n1,n2,m0=0,equal.variance=FALSE)
{
    if( equal.variance==FALSE ) 
    {
        se <- sqrt( (s1^2/n1) + (s2^2/n2) )
        # welch-satterthwaite df
        df <- ( (s1^2/n1 + s2^2/n2)^2 )/( (s1^2/n1)^2/(n1-1) + (s2^2/n2)^2/(n2-1) )
    } else
    {
        # pooled standard deviation, scaled by the sample sizes
        se <- sqrt( (1/n1 + 1/n2) * ((n1-1)*s1^2 + (n2-1)*s2^2)/(n1+n2-2) ) 
        df <- n1+n2-2
    }      
    t <- (m1-m2-m0)/se 
    dat <- c(m1-m2, se, t, 2*pt(-abs(t),df))    
    names(dat) <- c("Difference of means", "Std Error", "t", "p-value")
    return(dat) 
}


## calculate ttest

ITT_blood.glucose_combined_time_subset_AUC_t.test <- t.test2(m1 = ITT_blood.glucose_combined_time_subset_AUC[1,1], 
                                                 m2 = ITT_blood.glucose_combined_time_subset_AUC[2,1], 
                                          s1 = ITT_blood.glucose_combined_time_subset_AUC[1,3], 
                                          s2 = ITT_blood.glucose_combined_time_subset_AUC[2,3],
                                          n1 = ITT_blood.glucose_combined_time_subset_AUC[1,4], 
                                          n2 = ITT_blood.glucose_combined_time_subset_AUC[2,4])

ITT_blood.glucose_combined_time_subset_AUC_t.test[4]
```




## PLOT

### ITT by time
```{r}
ITT_blood.glucose_plot <- ITT_blood.glucose_SUMM %>%
  mutate(time = as.numeric(str_remove(time, "time_")),
         simple_geno_n = paste0(simple_geno, "\nn = ", n),
         simple_geno_n = factor(simple_geno_n, levels = c("Controls\nn = 9", "Nkx2.2fl/fl\nGcg-iCre\nn = 8"),
                                labels = c("Controls\nn = 9", "Nkx2.2fl/fl;Gcg-iCre\nn = 8"))) %>%
  ggplot(aes(x = time, y = mean_BG, color = simple_geno_n)) +
  geom_point(size = 4) +
  geom_line(size = 2) +
  geom_errorbar(aes(ymin = mean_BG - se, ymax = mean_BG + se), width=2,
                 position=position_dodge(.9),
                color = "black") +
  cowplot::theme_cowplot() +
  labs(x = "Time Post Insulin Injection (minutes)",
       y = "Mean Blood Glucose (mg/dL)",
       color = "Genotype",
       title = "Insulin Tolerance Test\nFollowing a 6 Hour Fast") +
  theme(axis.title = element_text(face = "bold")) +
  scale_color_manual(values = c("#bdbdbd", "#41ab5d")) +
  scale_x_continuous(breaks = c(0, 15, 30, 60, 90, 120)) +
  ylim(0, 200)
  
  

tiff("/Volumes/Elliott_Brooks/backup/ITT/plots/ITT_blood.glucose_plot.tiff", 
     units = "in", width = 6, height = 4, 
     res = 300, compression = "lzw")
ITT_blood.glucose_plot
dev.off()


pdf("/Volumes/Elliott_Brooks/backup/ITT/plots/ITT_blood.glucose_plot.pdf", 
     width = 6, height = 4)
ITT_blood.glucose_plot
dev.off()

```

### AUC

#### all time points
```{r}
ITT_blood.glucose_combined_AUC_plot <- ITT_blood.glucose_combined_AUC %>%
  mutate(genotype = factor(genotype, levels = c("Controls", "Nkx2.2fl/fl\nGcg-iCre"),
                                labels = c("Controls", "Nkx2.2fl/fl;\nGcg-iCre"))) %>%
  ggplot(aes(x = genotype, y = AUC, fill = genotype)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  ggsignif::geom_signif(comparisons = list(c(1,2)),
                        annotations = paste0("p = ", 
                                             as.character(signif(ITT_blood.glucose_combined_AUC_t.test[4], 
                                                                         digits = 3))),
                        y_position = 10500,
                        tip_length = 0) +
  cowplot::theme_cowplot() +
  labs(x = "Time Post Insulin Injection (minutes)",
       y = "Area Under the Curve",
       color = "Genotype") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        legend.position = "none",
        axis.title.x = element_blank()) +
  scale_fill_manual(values = c("#bdbdbd", "#41ab5d"))
  

tiff("/Volumes/Elliott_Brooks/backup/ITT/plots/ITT_blood.glucose_combined_AUC_plot.tiff", 
     units = "in", width = 3, height = 4, 
     res = 300, compression = "lzw")
ITT_blood.glucose_combined_AUC_plot
dev.off()


pdf("/Volumes/Elliott_Brooks/backup/ITT/plots/ITT_blood.glucose_combined_AUC_plot.pdf", 
     width = 3, height = 4)
ITT_blood.glucose_combined_AUC_plot
dev.off()
```

#### 30-90 min.
```{r}
ITT_blood.glucose_combined_AUC_30.90_plot <- ITT_blood.glucose_combined_time_subset_AUC %>%
  mutate(genotype = factor(genotype, levels = c("Controls", "Nkx2.2fl/fl\nGcg-iCre"),
                                labels = c("Controls", "Nkx2.2fl/fl;\nGcg-iCre"))) %>%
  ggplot(aes(x = genotype, y = AUC, fill = genotype)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  ggsignif::geom_signif(comparisons = list(c(1,2)),
                        annotations = paste0("p = ", 
                                             as.character(signif(ITT_blood.glucose_combined_time_subset_AUC_t.test[4], 
                                                                         digits = 3))),
                        y_position = 5000,
                        tip_length = 0) +
  cowplot::theme_cowplot() +
  labs(x = "Time Post Insulin Injection (minutes)",
       y = "Area Under the Curve",
       color = "Genotype") +
  theme(axis.title = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        legend.position = "none",
        axis.title.x = element_blank()) +
  scale_fill_manual(values = c("#bdbdbd", "#41ab5d"))
  

tiff("/Volumes/Elliott_Brooks/backup/ITT/plots/ITT_blood.glucose_combined_AUC_30.90_plot.tiff", 
     units = "in", width = 3, height = 4, 
     res = 300, compression = "lzw")
ITT_blood.glucose_combined_AUC_30.90_plot
dev.off()


pdf("/Volumes/Elliott_Brooks/backup/ITT/plots/ITT_blood.glucose_combined_AUC_30.90_plot.pdf", 
     width = 3, height = 4)
ITT_blood.glucose_combined_AUC_30.90_plot
dev.off()
```

