---
title: "Brissova_alphaT1D_DGE.analysis"
author: "Elliott Brooks"
date: "7/20/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)


library(clusterProfiler)
library(org.Hs.eg.db)
library(RColorBrewer)
library(cowplot)
library(ggrepel)
library(ggvenn)
library(pheatmap)
library(viridis)



library("DESeq2")
library(ggrepel)
library(readxl)
library(dplyr)
library(readr)
library(ggrastr)

library(data.table)

source("/Volumes/Brooks_02/Analysis/Brooks_etal_2024/Functions_2024/functionfile_Brooks_2024.R")

```

# Data import

- Counts table for RNA-seq of human alpha cells from individuals with and without T1D was downloaded off of the NIH Geo database but was published here:

Brissova, M., Haliyur, R., Saunders, D., Shrestha, S., Dai, C., Blodgett, D.M., Bottino, R., Campbell-Thompson, M., Aramandla, R., Poffenberger, G. and Lindner, J., 2018. α cell function and gene expression are compromised in type 1 diabetes. Cell reports, 22(10), pp.2667-2676.

- Differential gene expression analysis of Nkx2.2 alpha cell KO cells and control alpha cells was done in another project in this repo named nkx2.2_KO_transcriptional_analysis

~/figure_2/src/nkx2.2_KO_transcriptional_analyses/nkx2.2_alpha_KO_invivo_RNAseq_DESeq.Rmd 

```{r}
# download counts table for alpha cell T1D RNAseq data
urld <- "https://www.ncbi.nlm.nih.gov/geo/download/?format=file&type=rnaseq_counts"
path <- paste(urld, "acc=GSE106148", "file=GSE106148_raw_counts_GRCh38.p13_NCBI.tsv.gz", sep="&");
tbl <- as.matrix(data.table::fread(path, header=T, colClasses="integer"), rownames=1)


#import Nkx2.2 KO alpha cell DGE output
Nkx2.2_invivo.alpha_KO_DESeq2_padj.filt <-
  read.csv("/Volumes/Brooks_02/Analysis/invivo_Nkx2.2_alpha_KO_RNAseq/results/output_data/Nkx2.2_invivo.alpha_KO_DESeq2_output_padj.filt.csv")

Nkx2.2_invivo.alpha_KO_DESeq2_output <-
  read.csv("/Volumes/Brooks_02/Analysis/invivo_Nkx2.2_alpha_KO_RNAseq/results/output_data/Nkx2.2_invivo.alpha_KO_DESeq2_output.csv")


```



# DESeq2: Perform Differtial Gene Expression analysis on the human alpha T1D RNA-seq

## Set metadata for analysis
```{r}

condition = c("non_DB", "non_DB","non_DB", "non_DB", "non_DB",
                 "T1D", "T1D", "T1D")
samples <- c("GSM2830482", "GSM2830483", "GSM2830484", "GSM2830485", "GSM2830486", "GSM2830487", "GSM2830488", "GSM2830489")



colData <- data.frame(row.names = samples, condition = condition)

colData$condition <- factor(colData$condition)

```

## Generate DESeq Dataset from counts matrix and metadata
```{r}
ddsHTSeq <- DESeqDataSetFromMatrix(countData = tbl,
             colData = colData,
             design = ~condition)

```


## Run differenital Analysis
```{r}

dds = DESeq(ddsHTSeq)

```

## Get differential expression results
```{r, Results 1}
#Get results from the dds_batch with adjusted p-value < 0.05
res <- results(dds)
table(res$padj!=0)
table(res$padj<0.05)

#Order the samples by the adjusted p-value
res = res[order(res$padj),]

#merge res with the normalized count data which allows you to view basemean normalized values for each sample
resdata = merge(as.data.frame(res), as.data.frame(counts(dds, normalized =TRUE)), by="row.names", sort = FALSE)

resdata_filt <- resdata %>% dplyr::filter(padj <= 0.05)
```

## convert entrez IDs into gene symbols
```{r}
names(resdata)[1]="entrezid"


symbols.entrezid2 <- bitr(resdata$entrezid, 
                  fromType = "ENTREZID", 
                  toType = "SYMBOL", 
                  OrgDb = "org.Hs.eg.db")

T1D.alpha_seq_foldchange <- resdata %>%
  left_join(., symbols.entrezid2, by = c("entrezid" = "ENTREZID"))


#write the results to a csv file 
write.csv(T1D.alpha_seq_foldchange, file="/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/output_data/Nkx2.2_aTC_KD_DESeq2_output_deseq2.csv")
```

## Filter DEG output by significance
```{r}

T1D.alpha_seq_padj <- T1D.alpha_seq_foldchange %>% 
  dplyr::filter(padj <= 0.05)

T1D.alpha_seq_pval <- T1D.alpha_seq_foldchange %>% 
  dplyr::filter(pvalue <= 0.01)

write.csv(T1D.alpha_seq_pval, file="/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/output_data/T1D.alpha_seq_pval.csv")

write.csv(T1D.alpha_seq_padj, file="/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/output_data/T1D.alpha_seq_padj.csv")
```


# convert human names to mouse names
```{r}
# download conversion table that has mouse and human gene homology equivalences 
Mm_Hs_convert <- fread('http://www.informatics.jax.org/downloads/reports/HOM_MouseHumanSequence.rpt') %>%
  mutate(`EntrezGene ID` = as.character(`EntrezGene ID`))


# create dataframes for joining homology data
Mm_Hs_convert_concise <- Mm_Hs_convert %>%
  dplyr::select(`DB Class Key`, `Common Organism Name`, `EntrezGene ID`) 

Mm_Hs_convert_mouse_join <- Mm_Hs_convert %>%
  dplyr::filter(`Common Organism Name` == "mouse, laboratory") %>%
  dplyr::select(`DB Class Key`, Symbol)



# join mouse homology data to human RNAseq DGE output

T1D.alpha_seq_pval_ms.symb <- T1D.alpha_seq_pval %>%
  mutate(entrezid = as.character(entrezid)) %>%
  left_join(., Mm_Hs_convert_concise, by = c("entrezid" = "EntrezGene ID")) %>%
  left_join(., Mm_Hs_convert_mouse_join, by = "DB Class Key")

write.csv(T1D.alpha_seq_pval_ms.symb,
          "/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/output_data/T1D.alpha_seq_pval_mouse.symbols.csv")




T1D.alpha_seq_padj_ms.symb <- T1D.alpha_seq_padj %>%
  mutate(entrezid = as.character(entrezid)) %>%
  left_join(., Mm_Hs_convert_concise, by = c("entrezid" = "EntrezGene ID")) %>%
  left_join(., Mm_Hs_convert_mouse_join, by = "DB Class Key")
  
write.csv(T1D.alpha_seq_padj_ms.symb,
          "/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/output_data/T1D.alpha_seq_padj_mouse.symbols.csv")



T1D.alpha_seq_foldchange_ms.symb <- T1D.alpha_seq_foldchange %>%
  mutate(entrezid = as.character(entrezid)) %>%
  left_join(., Mm_Hs_convert_concise, by = c("entrezid" = "EntrezGene ID")) %>%
  left_join(., Mm_Hs_convert_mouse_join, by = "DB Class Key") %>%
  dplyr::filter(!is.na(pvalue))
  
write.csv(T1D.alpha_seq_foldchange_ms.symb,
          "/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/output_data/T1D.alpha_seq_foldchange_ms.symb.csv")
```

# Integrative analsysis: overlap between T1D and Nkx2.2 KO alpha genes

## find overlaps between datasets
```{r}

T1D.alpha_seq_pval_ms.symb_conscise <- T1D.alpha_seq_pval_ms.symb %>%
  dplyr::select(Symbol, SYMBOL, log2FoldChange, pvalue, padj)


colnames(T1D.alpha_seq_pval_ms.symb_conscise)[1:2] <- c("mouse_symbol", "human_symbol")

nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes <- Nkx2.2_invivo.alpha_KO_DESeq2_padj.filt %>%
  dplyr::select(symbol, log2FoldChange, padj) %>%
  left_join(., T1D.alpha_seq_pval_ms.symb_conscise, by = c("symbol" = "mouse_symbol")) %>%
  mutate(T1D_overlap = if_else(!is.na(human_symbol),
                               "T1D_overlap",
                               "no_overlap"))
#######

T1D.alpha_seq_padj_ms.symb_conscise <- T1D.alpha_seq_padj_ms.symb %>%
  dplyr::select(Symbol, SYMBOL, log2FoldChange, pvalue, padj)


colnames(T1D.alpha_seq_padj_ms.symb_conscise)[1:2] <- c("mouse_symbol", "human_symbol")

nkx2.2_alpha_KO_seq_foldchange_FDR_padj.T1Dgenes <- Nkx2.2_invivo.alpha_KO_DESeq2_padj.filt %>%
  dplyr::select(symbol, log2FoldChange, padj) %>%
  left_join(., T1D.alpha_seq_padj_ms.symb_conscise, by = c("symbol" = "mouse_symbol")) %>%
  mutate(T1D_overlap = if_else(!is.na(human_symbol),
                               "T1D_overlap",
                               "no_overlap"))
```

## Summary dataframes

```{r}
nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_SUMM <- nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes %>%
  group_by(T1D_overlap) %>%
  summarize(count = n())


nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_padj_SUMM <- nkx2.2_alpha_KO_seq_foldchange_FDR_padj.T1Dgenes %>%
  group_by(T1D_overlap) %>%
  summarize(count = n())

```



## STATISTICS

```{r}
# create contingency table for T1D data
T1D.alpha_seq_foldchange_stat <- T1D.alpha_seq_foldchange %>%
  mutate(diff.expression = if_else(pvalue <= 0.01,
                                   "DEG",
                                   "not_different")) %>%
  dplyr::filter(!is.na(pvalue)) %>%
  group_by(diff.expression) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(names = "T1D_alpha") %>%
  pivot_wider(names_from = diff.expression, values_from = count) 


colnames(T1D.alpha_seq_foldchange_stat)[2:3] <- c("count", "background_count")

# create contingency table for Nkx2.2 alpha KO data
nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_STAT <- 
  nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_SUMM %>%
  ungroup() %>%
  mutate(names = "Nkx2.2_KO_alpha") %>%
  pivot_wider(names_from = T1D_overlap, values_from = count)

colnames(nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_STAT)[2:3] <- c("count", "background_count")


# combine cont. tables into one table
Nkx2.2_KO_T1D.alpha_overlap_STAT <- rbind(T1D.alpha_seq_foldchange_stat, 
      nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_STAT)

# perform hypergeometric test using my function.
Nkx2.2_KD_T1D.alpha_overlap_STAT_outpt <- manyFishR(Nkx2.2_KO_T1D.alpha_overlap_STAT)



####### padj

# create contingency table for T1D data
T1D.alpha_seq_foldchange_stat_padj <- T1D.alpha_seq_foldchange %>%
  mutate(diff.expression = if_else(padj <= 0.05,
                                   "DEG",
                                   "not_different")) %>%
  dplyr::filter(!is.na(padj)) %>%
  group_by(diff.expression) %>%
  summarize(count = n()) %>%
  ungroup() %>%
  mutate(names = "T1D_alpha") %>%
  pivot_wider(names_from = diff.expression, values_from = count) 


colnames(T1D.alpha_seq_foldchange_stat_padj)[2:3] <- c("count", "background_count")


# create contingency table for Nkx2.2 alpha KO data
nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_padj_STAT <- 
  nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_padj_SUMM %>%
  ungroup() %>%
  mutate(names = "Nkx2.2_KO_alpha") %>%
  pivot_wider(names_from = T1D_overlap, values_from = count)

colnames(nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_padj_STAT)[2:3] <- c("count", "background_count")



# combine cont. tables into one table
Nkx2.2_KO_T1D.alpha_overlap_padj_STAT <- rbind(T1D.alpha_seq_foldchange_stat_padj, 
      nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_padj_STAT)

# perform hypergeometric test using my function.
Nkx2.2_KD_T1D.alpha_overlap_padj_STAT_outpt <- manyFishR(Nkx2.2_KO_T1D.alpha_overlap_padj_STAT)

```



# Plots

## Volcano plot

- plots shows DGEs from Nkx2.2KO alpha cells with DGEs that were also dysregulated in alpha cells from T1D individuals colored in blue.
- important overlaps are labled.

### Tidy data for plotting
```{r}

nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_join <- nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes %>%
  dplyr::select(symbol, T1D_overlap)

Nkx2.2_invivo.alpha_KO_DESeq2_output_T1D.genes <- Nkx2.2_invivo.alpha_KO_DESeq2_output %>%
  left_join(., nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes_join) %>%
  mutate(T1D_overlap = replace_na(T1D_overlap, "no_overlap"),
         T1D_overlap = if_else(symbol == "Gcg",
                               "T1D_overlap",
                               T1D_overlap))

```

### make lists of import overlap genes that appear in both datasets
```{r}

T1D_genes_down <- c("Gpr119", "Mafb", "Slc38a4", "Robo2", "Avpr1b", "Etv1", "Slc30a8", "Gcg")

T1D_genes_up <- c("Chgb",  "Cacna1i", "Isl1", "Insig1", "Gprc5b", "Ins1", "Ins2", "Iapp")

```

### generate volcano plot
```{r}

alpha_Nkx2.2_KO_RNAseq_T1D.genes_volcano_plot <- Nkx2.2_invivo.alpha_KO_DESeq2_output_T1D.genes %>%
  dplyr::filter(log2FoldChange < 4 & log2FoldChange > -4,
                -log10(padj) < 40) %>%
  mutate(sig = if_else(padj <= 0.05 & !is.na(padj),
                               "significant",
                               "not_sig"),
         T1D_overlap = factor(T1D_overlap,
                              levels = c("T1D_overlap",
                                         "no_overlap"),
                              labels = c("T1D_overlap" = "T1D Affected Gene",
                                         "no_overlap" = "Not Affected"))) %>%
  arrange(desc(T1D_overlap)) %>%
ggplot(aes(x = log2FoldChange, y = -log10(padj), 
           color = T1D_overlap, 
           size = T1D_overlap)) + 
  geom_point() +
  geom_text_repel(data = Nkx2.2_invivo.alpha_KO_DESeq2_output_T1D.genes, 
                  aes(label = if_else(symbol %in% T1D_genes_down, 
                                symbol,
                                "")), 
            color = "black", 
            max.overlaps = Inf,
            point.padding = .6,
            box.padding = 1.1,
            nudge_x = -1.25,
            force_pull = 0.5,
            size = 4,
            fontface = "bold",
            min.segment.length = 0,
            seed = 42) +
  geom_text_repel(data = Nkx2.2_invivo.alpha_KO_DESeq2_output_T1D.genes, 
                  aes(label = if_else(symbol %in% T1D_genes_up, 
                                symbol,
                                "")), 
            color = "black", 
            max.overlaps = Inf,
            point.padding = .6,
            box.padding = 1.1,
            nudge_x = 1.25,
            force_pull = 0.5,
            size = 4,
            fontface = "bold",
            min.segment.length = 0,
            seed = 43) +
  cowplot::theme_cowplot() +
  scale_color_manual(values = c("T1D Affected Gene" = "#2b8cbe" ,
                                "Not Affected" = "#bdbdbd")) +
  scale_size_manual(values = c("T1D Affected Gene" = 3,
                                "Not Affected" = 2)) +
  labs(y = "Significance (-log10(adjusted p-value))",
       color = "T1D-related Gene Overlap") +
  theme(aspect.ratio = 1,
        axis.title = element_text(face = "bold")) +
  xlim(-4.5, 4.5) +
  ylim(0,32) +
  guides(size = "none")


# rasterize dots in scatter plot for easier use in adobe illustrator
alpha_Nkx2.2_KO_RNAseq_T1D.genes_volcano_plot_rastr <- rasterize(alpha_Nkx2.2_KO_RNAseq_T1D.genes_volcano_plot, 
                                                                 layers = "Point", dpi = 300)
  

# Export

tiff("/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/plots/alpha_Nkx2.2_KO_RNAseq_T1D.genes_volcano_plot.tiff", 
     units = "in", width = 8, height = 8, 
     res = 300, compression = "lzw")
alpha_Nkx2.2_KO_RNAseq_T1D.genes_volcano_plot
dev.off() 

pdf("/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/plots/alpha_Nkx2.2_KO_RNAseq_T1D.genes_volcano_plot.pdf", 
     width = 8, height = 8)
alpha_Nkx2.2_KO_RNAseq_T1D.genes_volcano_plot_rastr
dev.off() 

```


## Venn diagram
- Venn diagram showing the overlap of DGEs found in Nkx2.2 KO alpha cells in mice and alpha cell from T1D Humans.
- p value in figure added in illustrator.
```{r}
# create vectors of DGEs in each data set
alpha_KO_DEG_list <- nkx2.2_alpha_KO_seq_foldchange_FDR_T1Dgenes$symbol %>% unique()

alpha_T1D_list <- T1D.alpha_seq_pval_ms.symb$Symbol %>% unique()

# merge vectors into a list for plotting
alpha_KO.DEG.T1D_list <- list("Nkx2.2 \u03B1 KO" = alpha_KO_DEG_list,
                            "T1D \u03B1 cells" = alpha_T1D_list)

# Plot Venn Diagram
alpha_KO.DEG.T1D_plot <- ggvenn(alpha_KO.DEG.T1D_list, 
                             show_percentage = FALSE, 
                             text_size = 12, 
                             fill_color = c("#74c476", "#3690c0"))

#export

tiff("/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/plots/Nkx2.2_KO_T1D.alpha_overlap_Venn.tiff", 
     units = "in", width = 6, height = 6, 
     res = 300, compression = "lzw")
alpha_KO.DEG.T1D_plot
dev.off() 

pdf("/Volumes/Elliott_Brooks/Brissova_alphaT1D_RNAseq/results/plots/Nkx2.2_KO_T1D.alpha_overlap_Venn.pdf", 
     width = 6, height = 6)
alpha_KO.DEG.T1D_plot
dev.off() 

```


